% main.tex --- unsolved-relay M6 manuscript draft
% Khinchin K_0 bounded two-tier null result
%
% Compile with:  pdflatex main && bibtex main && pdflatex main && pdflatex main
% Bibliography:  references.bib (paper-read-verified entries only)
% Preflight compliance: see paper/preflight_compliance.md
%
% Authority chain (gold tags on origin/main of github.com/papanokechi/khinchin-k0-bounded):
%   gold/M1 = 15b216f   (target frozen)
%   gold/M2 = ca9c989   (M2.3 predicate frozen)
%   gold/M3 = 9c2702d   (canonical JSONL outputs frozen)
%   gold/M4 = fd13eeb   (capability-gap document frozen)
%   gold/M5 = 208f6fc   (Lean 4 skeleton + axiom set frozen)
%
% Manuscript drafting commit base: HEAD at b08162a (M6 Step 1 H8 paper-read complete).

\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{longtable}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  citecolor=blue!50!black,
  urlcolor=blue!50!black
}
\setlength{\emergencystretch}{3em}
\sloppy

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  frame=single,
  framesep=4pt,
  xleftmargin=4pt,
  xrightmargin=4pt
}

\newcommand{\K}{K_{0}}
\newcommand{\Hrig}{H_{\mathrm{rigorous}}}
\newcommand{\Hemp}{H_{\mathrm{empirical}}}
\newcommand{\Hempop}{H_{\mathrm{empirical}}^{\mathrm{op}}}
\newcommand{\Hempfo}{H_{\mathrm{empirical}}^{\mathrm{fo}}}
\newcommand{\BDC}{B_{D}(C)}
\newcommand{\fsp}{\textsf{field\_standard\_practice}}
\newcommand{\pc}{\textsf{proven\_corollary}}
\newcommand{\rt}{\textsf{rigorous\_theorem}}
\newcommand{\eh}{\textsf{empirical\_heuristic}}

\title{A bounded two-tier null result for integer relations on a hybrid
  Khinchin-$\K$ basis,\\ with a documented capability gap and a Lean~4
  statement-shape encoding}
\author{[Author]\thanks{Repository: \url{https://github.com/papanokechi/khinchin-k0-bounded}. Canonical
  artifacts are tagged \texttt{gold/M1}--\texttt{gold/M5} on \texttt{origin/main}.}}
\date{Draft: \today}

\begin{document}
\maketitle

\begin{abstract}
We test for integer relations on the hybrid basis
$\BDC = \{1, \K, \K^{2}, \ldots, \K^{D}, \log\K\} \cup \{\K\cdot c : c \in C\}$
at $D=6$ and
$C=\{\pi, e, \log 2, \gamma, \zeta(2), \zeta(3), G\}$
(dimension $n=15$).
A cascading-precision PSLQ harness based on \texttt{mpmath.pslq} at
$P=2160$~dps with cascade legs at $2P$ and $4P$
returns a cascade-stable null on all $65$ scanned sub-bases,
independently corroborated by a PARI/GP \texttt{lindep} second leg.
We report the null at two complementary tiers under an explicit
verification-class taxonomy (\fsp{}, \pc{}):
the empirical tier bounds the coefficient height
$\Hempop \approx 7.997 \times 10^{69}$ at the Bailey--Borwein--Crandall (1997)
confidence calibration~\cite{bbc1997}, classified \fsp{} per the
Bailey--Plouffe (1998) ``general rule'' for PSLQ
detection~\cite{bailey1998};
the rigorous tier bounds the relation Euclidean norm
$\Hrig = 1.0361 \times 10^{72}$ via the
Ferguson--Bailey--Arno (1999) Theorem~1 and Corollary~2
overshoot--free framework~\cite{fba1999}, classified \pc{}
(implying $\max_{i}|m_{i}| \ge \Hrig/\sqrt{n} \approx 2.676 \times 10^{71}$).
Three Excluded Families
delineate this bounded scope from
(EF1) the BBC 1997 pure-power null,
(EF2) the operator's prior signature-statistic null on $\pi$'s continued
fraction~\cite{papanokechi2026signature},
and (EF3) Gauss--Kuzmin--Wirsing spectral-method imports.
A symbolic-closure attempt in \texttt{SymPy} surveying seven candidate structural
arguments (Lindemann--Weierstrass, Schanuel, Nesterenko, Mahler-measure, Galois,
non-GKW CF-theoretic, height theory) plus a four-path probe returned a documented
fundamental capability gap, rooted in $\K$'s unresolved transcendence status.
The result statement is additionally encoded in Lean~4 with an explicit
auxiliary-axiom trust boundary; the encoding type-checks against Mathlib4
v4.14.0 but is not a first-principles formal proof.
\end{abstract}

%======================================================================
\section{Introduction}
%======================================================================

Khinchin's constant
\[
  \K \;\approx\; 2.6854520010653064453097148\ldots
\]
is the almost-everywhere geometric mean of partial quotients of the regular
continued-fraction expansion of a real number~\cite{khinchin1934}.
The constant is computable to arbitrary precision via classical accelerated
series, but its arithmetic nature is open: no published proof of
irrationality, algebraicity, or transcendence exists as of this writing.
The standard expectation in the transcendence literature is that $\K$ is
transcendental; every published attack on irrationality has stalled at
infrastructure questions rather than a clean obstruction.

\paragraph{The bounded sub-question.}
We test, at working precision $P = 2160$ decimal places via PSLQ with a
cascading-precision harness, for integer relations among the hybrid basis
\begin{equation}\label{eq:basis}
  \BDC \;=\; \bigl\{1,\, \K,\, \K^{2}, \ldots,\, \K^{D},\, \log\K\bigr\}
  \;\cup\;
  \bigl\{\K \cdot c \;:\; c \in C\bigr\}
\end{equation}
with
\begin{equation}\label{eq:cset}
  D \;=\; 6, \qquad
  C \;=\; \bigl\{\pi,\, e,\, \log 2,\, \gamma,\, \zeta(2),\, \zeta(3),\, G\bigr\},
  \qquad
  n \;=\; \dim \BDC \;=\; 15,
\end{equation}
with a coefficient bound $H$ specified at two tiers in
Section~\ref{sec:methods} below (the empirical tier as a coefficient-height
bound; the rigorous tier as a Euclidean-norm bound with implied
coefficient-height bound).
The bounded sub-question has two terminal outcomes: a positive result
(PSLQ returns a relation surviving cascade and independent verification)
or a negative result (cascade-stable null with an explicit pair of height
bounds and verification classes).
Both terminal outcomes are first-class deliverables under the mission's
explicit-evidence-acceptance-and-logging discipline.

\paragraph{Prior art and the named-open complement.}
This work sits inside a small ecosystem of prior numerical attacks on $\K$'s
arithmetic relations.
We anchor the scope on two paper-read-verified citations and one explicit
methodological-cede:

\begin{enumerate}[label=(\arabic*),itemsep=2pt,topsep=2pt]
\item Bailey, Borwein, and Crandall~\cite{bbc1997}
  (henceforth ``BBC~1997'') tested at the parameters
  $(D{=}50, H{=}10^{70}, 7350~\text{dps})$
  the pure-power basis $\{1, \K, \K^{2}, \ldots, \K^{50}\}$
  and reported a cascade-stable null (Test~1, \S 4).
  BBC's \S 4 close names
  \emph{``log $\K$, $(\log\K)(\log 2)$, or one of many other forms involving $\K$''}
  as open.
  This open passage is the named complement that the present basis
  $\BDC$ explicitly targets.

\item The operator's prior work~\cite{papanokechi2026signature}
  (henceforth ``the signature paper'') tested, at $300$~dps base with
  $600$~dps confirmation, the signature-statistic family
  $\{S_{n}, \log S_{n}, S_{n}-\K, \log n\}$ on $\pi$'s continued-fraction
  partial-quotient sequence at $\textsf{maxcoeff}=10^{3}$,
  with $546$ attempts and a $10^{6}$ wide-cap diagnostic, returning a
  precision-controlled null.
  The Discussion section of that paper handed off, verbatim:
  \emph{``Templates involving $n^{1/2}$, $n^{2}$, or algebraic combinations
  of $\K$ with other known constants lie entirely outside the tested
  family and remain open.''}
  The present basis $\BDC$ is precisely that
  ``algebraic-combinations-with-other-known-constants'' extension under the
  same AEAL discipline.

\item The Gauss--Kuzmin--Wirsing spectral framework, while theoretically
  connected to $\K$ via the transfer-operator point of view, is ceded
  methodologically: theoretical citation is permitted; method-import is
  prohibited per a mission-internal binding.
  This binding is mission-procedural; it neither weakens nor strengthens
  the present numerical claims.
\end{enumerate}

These three prior areas form the three Excluded Families (EF1, EF2, EF3)
defined formally in Section~\ref{sec:methods}.
The mission-relevant complement is the union
\begin{equation}\label{eq:complement}
  \BDC \setminus (\text{EF1} \cup \text{EF2} \cup \text{EF3})
\end{equation}
i.e.\ the rows $\log\K$ and $\K\cdot c$ for $c \in C$ together with all
hybrid combinations crossing the pure-power and log/bilinear sub-blocks.

\paragraph{The contribution.}
The contribution of this manuscript is twofold and intentionally narrow:
\begin{enumerate}[label=(\alph*),itemsep=2pt,topsep=2pt]
\item \textbf{A two-tier bounded null on the named-open complement of
  Eq.~\eqref{eq:complement}.}
  At the height where BBC~1997 reported a single-tier empirical null on a
  \emph{different} basis (the EF1 pure-power family), this work reports a
  \emph{two-tier} null on the full basis $\BDC$ (which \emph{includes} the
  named-open EF1-complement rows): empirical
  $\Hempop \approx 7.997\times 10^{69}$ (\fsp{}, BBC-class height
  bound at the primary $n=15$ sub-basis, where the operational cap is
  inactive) and rigorous
  $\Hrig = 1.0361\times 10^{72}$ (\pc{}, FBA~1999 Theorem~1 + Corollary~2;
  bounds the Euclidean norm of any non-trivial integer relation, which by
  $\|m\|_{2} \le \sqrt{n}\,\max_{i}|m_{i}|$ implies the coefficient-height
  bound $\max_{i}|m_{i}| \ge \Hrig/\sqrt{15} \approx 2.676\times 10^{71}$).
  This is not a bound-beating result on the same basis; it is a
  \emph{stronger-class} result on a basis-class BBC named open.

\item \textbf{A documented capability gap, and an explicit Lean~4 trust
  boundary.}
  A symbolic-closure attempt for the null result surveyed seven candidate
  structural arguments (Lindemann--Weierstrass, Schanuel, Nesterenko,
  Mahler-measure, Galois, non-GKW CF-theoretic, height theory) and ran a
  four-path probe in \texttt{SymPy} 1.14.0.
  All seven candidates fail at a shared root: $\K$'s transcendence status
  is itself the major open question in this corner of the literature, and any
  certificate strong enough to rule out integer relations in $\BDC$
  would imply progress on that question.
  We classify this as a fundamental capability gap, not a contingent
  machinery-availability problem.
  In parallel, the result statement is encoded in Lean~4 with an explicit
  auxiliary-axiom trust boundary; the encoding type-checks against Mathlib4,
  but is not a first-principles formal proof of the null.
  Statement-shape encoding with explicit trust boundary makes the implicit
  assumptions of the two-tier predicate machine-readable.
\end{enumerate}

We further report, as a small methodological contribution, an
operational-bound capping observation: the BBC empirical-scaling formula
$H \approx c \cdot 10^{P/(c\,n)}$
extrapolates outside the PSLQ-with-\textsf{maxcoeff} search range at small
$n$, so the operational empirical bound must be reported as
$\min(\text{formula}, 10^{\log_{10}\textsf{maxcoeff}})$
to remain testable.

\paragraph{Outline.}
Section~\ref{sec:methods} fixes the two-tier predicate, the harness
architecture, the verification-class taxonomy, the PSLQ algorithm citation
chain, and the Lean~4 scope statement.
Section~\ref{sec:results} reports the numerical outcomes:
the $65$-sub-basis empirical sweep, the primary cascade reproducibility, the
PARI/GP second-leg agreement, and the two-tier bounds with H9 verification
classes.
Section~\ref{sec:discussion} discusses the operational-bound capping
observation, the M4 fundamental capability gap with its
structurally-unavailable / scope-ceded sub-classification, and the
basis-class distinction with respect to BBC~1997.
Appendix~\ref{app:reproducibility} provides reproducibility data;
Appendix~\ref{app:aeal} describes the mission's heuristic-accumulation
methodology as a small but real meta-contribution.

%======================================================================
\section{Methods}\label{sec:methods}
%======================================================================

\subsection{Basis construction and three Excluded Families}\label{sec:basis-ef}

The basis $\BDC$ in Eq.~\eqref{eq:basis} is a hybrid of three sub-blocks:
the pure-power tower $\{1, \K, \K^{2}, \ldots, \K^{D}\}$ (dimension $D+1=7$),
the singleton $\{\log\K\}$ (dimension $1$), and the bilinear set
$\{\K\cdot c : c \in C\}$ (dimension $|C|=7$), for a total of $n=D+1+1+|C|=15$.
The Excluded Families partition the mission-relevant scope as follows.

\paragraph{EF1 (BBC-grandfathered pure-power subset).}
EF1 is the linear span of $\{1, \K, \K^{2}, \ldots, \K^{D}\}$.
A relation lying entirely in EF1 reproduces, at strictly weaker parameters
$(D{\le}6 \text{ vs.\ } D{\le}50,\;P{=}2160 \text{ vs.\ } 7350\;\text{dps})$,
the BBC~1997 \S 4 Test~1 null.
Such a finding is logged as a BBC-reproduction diagnostic rather than a
primary result.

\paragraph{EF2 (signature-paper-grandfathered).}
EF2 is the signature-statistic family on $\pi$'s continued fraction
$\{S_{n}, \log S_{n}, S_{n}-\K, \log n\}$.
By construction $\BDC$ contains no element of EF2; the harness does not test it.
The signature paper~\cite{papanokechi2026signature} is the legitimacy anchor
for the present extension.

\paragraph{EF3 (GKW-method-ceded).}
EF3 covers methodological imports from the Gauss--Kuzmin--Wirsing transfer-operator
spectral theory.
Theoretical citation is permitted; method-import is prohibited.
If PSLQ surfaces a relation whose interpretation requires GKW machinery, the
harness halts and the relation routes to the mission's mutation log for
operator review rather than into this manuscript.

\subsection{The two-tier predicate}\label{sec:two-tier}

A run of the harness on a sub-basis $B \subseteq \BDC$ produces a
\emph{cascade-stable null} if
\texttt{mpmath.pslq} returns \texttt{None} on $B$ at all three precisions
$\{P, 2P, 4P\} = \{2160, 4320, 8640\}$ dps with the same
\textsf{maxcoeff} bound $10^{70}$ and the H9 maxsteps schedule (Section
\ref{sec:harness}), AND a second-leg PARI/GP \texttt{lindep} run on $B$
returns either no relation or a relation whose largest coefficient exceeds
the empirical operational height $\Hempop$.

For a cascade-stable null we report at two height tiers under the H9
verification-class taxonomy (Section~\ref{sec:h9}):

\paragraph{Tier 1 --- empirical, classified \fsp{}.}
At BBC-1997 confidence calibration, no integer relation among the basis
elements has all coefficients of size $\le \Hemp$, where
\begin{equation}\label{eq:Hemp}
  \Hemp \;=\; c \cdot 10^{P/(c\,n)},\qquad c \approx 2.06,\;P=2160,\;n=15
  \;\Rightarrow\; \Hemp \;\approx\; 7.997\times 10^{69}.
\end{equation}
The operational tier is the capped value
$\Hempop = \min(\Hemp, 10^{\log_{10}\textsf{maxcoeff}}) = \min(\Hemp, 10^{70})$;
both are reported (Section~\ref{sec:results-bounds}).
The verification class \fsp{} reflects that the bound $H \approx c\cdot 10^{P/(c\,n)}$
is community-validated empirical practice (the BBC c-calibration over the
bare Bailey--Plouffe ``general rule'' of \cite[\S 2]{bailey1998}, see Section
\ref{sec:h9}), not a theorem of the underlying algorithm.

\paragraph{Tier 2 --- rigorous, classified \pc{}.}
At the FBA~1999 Theorem~1 + Corollary~2 conservative form, every non-trivial
integer relation $m$ among the basis elements has Euclidean norm
$\|m\|_{2} \ge \Hrig$, where $\Hrig$ is the largest value the per-iteration
lower-bound certificate
$M = 1/\max_{i,j}|H_{i,j}|$
attains across the cascade, scaled by mpmath's documented
integer-truncation safety factor:
\begin{equation}\label{eq:Hrig}
  \Hrig \;=\; 100 \cdot \max_{k \in \mathrm{cascade}} \mathrm{reported\_norm}_{k}.
\end{equation}
The convention $\|\cdot\|_{2}$ for the relation norm follows the
verbatim Step~5 statement of \cite[\S 2]{bailey1998}:
\emph{``there can exist no relation vector whose Euclidean norm is less
than $M$''}; the per-iteration certificate is the
\cite[Theorem~1]{fba1999} bound $M_{x} \ge 1/\max_{i}|h_{i,i}|$ on the
smallest relation Euclidean norm.
Equivalently, since
$\|m\|_{2} \le \sqrt{n}\,\max_{i}|m_{i}|$,
the coefficient-height bound implied by Tier~2 is
$\max_{i}|m_{i}| \ge \Hrig/\sqrt{n}$ at the relevant sub-basis dimension.
The verification class \pc{} reflects that \cite[Theorem~1]{fba1999} is a
\rt{}-class result and Eq.~\eqref{eq:Hrig} is its conservative
proven-corollary application.

\subsection{Algorithm-chain citation and {\boldmath$\gamma$} boundary
   case}\label{sec:algo-chain}

The chain from this manuscript's bound back to the underlying theorem
runs through four citations:
\begin{equation}\label{eq:chain}
\begin{aligned}
  \text{\texttt{mpmath.pslq}}
  &\;\longrightarrow\;
  \text{Bailey--Plouffe 1998 \S 2~\cite{bailey1998}} \\
  &\;\longrightarrow\;
  \text{FBA 1992 preprint}
  \;\longrightarrow\;
  \text{Ferguson--Bailey--Arno 1999~\cite{fba1999}}.
\end{aligned}
\end{equation}
\texttt{mpmath.pslq}'s docstring cites
\cite[\S 2]{bailey1998} verbatim
(URL
\url{http://www.cecm.sfu.ca/organics/papers/bailey/paper/html/node3.html};
SHA-256 hashes recorded in Appendix~\ref{app:reproducibility});
\cite[\S 2]{bailey1998} explicitly presents PSLQ in its
``simpler formulation'' and cites the Ferguson--Bailey complex PSLQ preprint
(circulated as a 1992 technical report) as its reference~[13],
the same algorithm that became~\cite{fba1999}.
The norm-bound certificate
$M = 1 / \max_{j} |H_{j}|$
appearing in \cite[\S 2 pseudocode step 5]{bailey1998}
is equivalent in conservative form to the per-iteration certificate
$M_{x} \ge 1 / \max_{i}|h_{i,i}(k)|$ of \cite[Theorem~1]{fba1999}.

The rigorous tier of this manuscript invokes \cite[Theorem~1]{fba1999} and
\cite[Corollary~2]{fba1999} specifically; it does \emph{not} invoke
\cite[Theorem~3]{fba1999} (the overshoot bound on PSLQ-found relations).
This matters because Theorem~3 carries a strict
$\gamma > \sqrt{4/3}$
condition (\cite[Definition~5]{fba1999}), while Theorems~1 and~2 hold at
the boundary $\gamma = \sqrt{4/3}$ by continuity.
The \texttt{mpmath.pslq} implementation chooses $\gamma = \sqrt{4/3}$
exactly internally (line
\texttt{g~=~sqrt\_fixed((4\textless\textless prec)//3, prec)}),
which lies inside the parameter scope explicitly treated in
\cite[\S 2]{bailey1998}.
We do not invoke Theorem~3.

\subsection{The H9 verification-class taxonomy and the
   Bailey--Plouffe ``general rule''}\label{sec:h9}

We report all numerical claims under a four-class verification taxonomy
(``H9'' in the mission's internal heuristic numbering): \rt{}, \pc{},
\fsp{}, \eh{}.
The class \fsp{} corresponds precisely to what \cite[\S 2]{bailey1998}
terms a ``general rule'' for PSLQ detection.
The relevant passage reads:
\begin{quote}
\emph{``As a general rule, one can expect to detect a relation of degree
$n$, with coefficients of size $10^{m}$, provided that the input vector
is known to somewhat greater than $m\cdot n$ digit precision.''}
\hfill\cite[\S 2]{bailey1998}
\end{quote}
This is the canonical statement of the
$H \approx 10^{P/n}$
empirical-scaling folklore; BBC~1997 calibrates the leading constant
$c \approx 2.06$ to absorb its ``somewhat greater than'' hedge.
The class \fsp{} formalizes this primary-source distinction: a community-validated
empirical scaling stated as a rule of practice, not as a theorem of PSLQ.

The class \pc{} is reserved for derivations from \cite[Theorem~1]{fba1999} or
\cite[Corollary~2]{fba1999} via mpmath's conservative
\texttt{norm //= 100}
truncation; these are theorem-grade up to the documented
$100\times$
safety factor.

\paragraph{Distinguishing the predicate class from the reported statistic.}
The H9 verification class assigned to a sub-basis record is a predicate-level
classification of the cascade-stable-null result for that sub-basis,
determined by which maxsteps schedule was in force at run time:
the rigorous-tier schedule
$(100\,000, 80\,000, 50\,000)$
is applied only to the primary $n=15$ cascade (one record), yielding
class \pc{}; the empirical-tier schedule
$(2000, 2000, 2000)$
is applied to the $64$ smaller sub-bases, yielding class \fsp{}.
The
$\Hrig$
column reported alongside every record is a statistic of the
\cite[Theorem~1]{fba1999} certificate evaluated at termination;
its numerical magnitude varies with the sub-basis but does not by itself
upgrade the record's predicate class.
The rigorous certificate
$\|m\|_{2} \ge \Hrig$
holds for every record where
$\Hrig > 0$,
but is reported as a \pc{}-class predicate result only for records run
under the rigorous-tier schedule.

\subsection{Harness architecture}\label{sec:harness}

The harness (\texttt{harness/verify.py} and \texttt{harness/sweep.py}) is
written against
\texttt{mpmath} 1.3.0 / Python 3.12.10
and shells out to PARI/GP 2.18.1 for the second leg.
Each candidate sub-basis $B$ runs in three phases:

\begin{enumerate}[itemsep=2pt,topsep=2pt]
\item \textbf{mpmath cascade.}
  $\texttt{mpmath.pslq}(B, \textsf{tol}=2^{-0.75 P}, \textsf{maxcoeff}=10^{70},
  \textsf{maxsteps}=\text{schedule}(n))$
  runs at $P = 2160$ dps, then at $2P$, then at $4P$.
  The cascade verdict is \emph{stable null} if all three legs return
  \texttt{None}; otherwise \emph{candidate} (further classified by
  Excluded-Family containment) or \emph{unstable} (transient PSLQ false positive).

\item \textbf{Rigorous-bound extraction.}
  \texttt{harness/rigorous\_bound.py} parses \texttt{mpmath.pslq}'s
  verbose-mode norm output to extract the per-iteration certificate of
  \cite[Theorem~1]{fba1999}, returning
  $\Hrig$ as in Eq.~\eqref{eq:Hrig}.
  The module docstring documents four divergences (D1--D4) between mpmath's
  internal form and the canonical \cite[Theorem~1]{fba1999} statement;
  divergences D1 and D4 are conservative (mpmath's bound is weaker than the
  canonical form), and divergences D2 and D3 are cleared by
  the paper-read of \cite[\S 2]{bailey1998} (Section~\ref{sec:algo-chain}).

\item \textbf{PARI/GP second leg.}
  \texttt{harness/gp\_lindep.py} writes the basis to a temporary file and
  invokes \texttt{gp -q --default parisize 4000000000} on a small script
  that returns the smallest \texttt{lindep} vector at the same precision.
  A second-leg \emph{noise-above-bound} verdict
  (\textsf{gp\_noise\_relation\_above\_H\_empirical\_confirms\_null})
  is recorded when the smallest \texttt{lindep} relation has
  $\max|m_{i}| > \Hempop$, confirming the null at the empirical tier.
\end{enumerate}

The cascade-stability check is non-collapsible: all three precision legs
must independently return \texttt{None} for the verdict.
mpmath's PSLQ implementation is deterministic at fixed precision and seed
on the build used here (\texttt{mpmath 1.3.0} on Python 3.12.10); see
Section~\ref{sec:repro-cascade}.

\subsection{Operational-bound capping clause}\label{sec:capping}

The BBC empirical-scaling formula
$\Hempfo = c\cdot 10^{P/(c\,n)}$
extrapolates outside the algorithm's \textsf{maxcoeff} search range at
small $n$ for our parameters:
at $P=2160$ dps, $c=2.06$, the formula evaluates to
$\approx 10^{524}$
at $n=2$ and
$\approx 10^{349}$
at $n=3$, both far above the
$\textsf{maxcoeff}=10^{70}$
search bound.
A PSLQ-with-\textsf{maxcoeff} run cannot detect any integer relation whose
largest coefficient exceeds \textsf{maxcoeff}, regardless of the formula's
extrapolation.
We therefore report the operational empirical bound as the cap
\begin{equation}\label{eq:cap}
  \Hempop \;=\; \min\bigl(\Hempfo,\; 10^{\log_{10}\textsf{maxcoeff}}\bigr).
\end{equation}
At the primary sub-basis $n=15$, the formula yields
$\Hempfo \approx 7.997\times 10^{69} < 10^{70}$,
so the cap is inactive and $\Hempop = \Hempfo$.
At small $n$, the cap activates and $\Hempop = 10^{70}$.
Both values are retained in the JSONL output for transparency
(see Section~\ref{sec:discussion}).

\subsection{Lean 4 statement-shape encoding}\label{sec:lean-scope}

The result statement is encoded in Lean~4 with documented auxiliary
axioms; the encoding type-checks against Mathlib4 v4.14.0.
Full formal verification requires further development beyond this
mission's scope.
The Lean~4 skeleton (approximately $385$ source lines across three modules
\texttt{M5/Definitions.lean}, \texttt{M5/Result.lean},
\texttt{M5/Axioms.lean}) makes the result's dependency structure
machine-readable: the axiom set behind
\texttt{m3\_null\_at\_rigorous\_bound}
is exactly
\begin{equation*}
  \begin{aligned}
    &\{\texttt{pslq\_cascade\_implies\_no\_integer\_relation}\}
    \;\cup\;
    \{\text{nine opaque constant axioms}\} \\
    &\hspace{1em}\cup\;
    \{\text{Lean core: \texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}}\},
  \end{aligned}
\end{equation*}
as recorded in \texttt{m5/\_print\_axioms\_output.txt} (committed at
\texttt{gold/M5 = 208f6fc}).

\paragraph{What the encoding IS and is NOT.}
Statement-shape Lean~4 encoding with explicit trust boundary is a
methodological contribution distinct from the numerical-and-rigorous-bound
$\K$ result: it makes the implicit assumptions of the two-tier predicate
explicit and machine-checkable.
The encoding is NOT a formal proof of the null result.
The M5 theorem discharges via
\texttt{exact pslq\_cascade\_implies\_no\_integer\_relation}
--- an \texttt{axiom} declaration, not a derivation.
We avoid the phrasing ``formally verified in Lean~4'' and ``Lean~4 proof of
the null result'' for this reason; the correct phrasing is
``statement-shape machine-checkable.''

\paragraph{Auxiliary-axiom enumeration.}
The trust boundary comprises four classes of axioms in
\texttt{m5/M5/}.
First, nine constant axioms (\texttt{realPi}, \texttt{realE},
\texttt{realLn2}, \texttt{zeta2}, \texttt{zeta3},
\texttt{eulerMascheroni}, \texttt{catalanConst}, \texttt{K0}, \texttt{logK0})
encode named real-valued constants as opaque \texttt{axiom} declarations
rather than imports from Mathlib's full constructions; this is a scope
simplification (Mathlib v4.14.0 provides
\texttt{Real.pi}, \texttt{Real.exp}, \texttt{Real.log} but not
\texttt{Real.catalan} or \texttt{Real.eulerMascheroni}).
Second, two evidence axioms (\texttt{pslq\_cascade\_implies\_no\_integer\_relation}
and \texttt{bbc\_empirical\_implies\_no\_integer\_relation}) encode the
load-bearing claims as axioms, not theorems; they are justified
informally by \cite[Theorem~1 + Corollary~2]{fba1999} and BBC~1997
respectively, but are not derived in Lean.
Third, one acknowledgement axiom (\texttt{M4\_fundamental\_gap}) is a
documentary placeholder whose role is only to provide a Lean-level handle
for the M4 fundamental-gap proposition (Section~\ref{sec:m4-gap}).
Fourth, one numerical-binding stub (\texttt{K0\_value\_first\_digits}) is
documentary only and not used by the result theorem.

\paragraph{Mathlib cache operational note.}
The Mathlib4 v4.14.0 package cache available to this work was a build
snapshot from a sibling project on the same machine.
Lake's \texttt{Replayed} mechanism re-uses pre-built \texttt{.olean} files
when their cryptographic trace-hash matches the expected hash; this is
fast (sub-second per module).
However, the cache contains only the import closure of the sibling project's
source files, not the full Mathlib library uniformly built.
An initial M5 implementation importing
\texttt{Mathlib.Data.Real.Pi.Bounds}
plus
\texttt{Mathlib.Analysis.SpecialFunctions.\{Log.Basic, Exp\}}
found $587$ modules replayed (matching the sibling project's import set) and
then began compiling modules outside that closure from scratch.
The mission resolved this operational scope by simplifying M5 imports to
\texttt{Mathlib.Data.Real.Basic}
plus
\texttt{Mathlib.Data.List.Basic}
(both inside the cache closure) and encoding the named constants as opaque
axioms as above.
The choice of opaque axioms for these constants is therefore not a defect
of the formalization but an operationally honest adaptation to the
available cache closure, consistent with the statement-shape scope.

%======================================================================
\section{Results}\label{sec:results}
%======================================================================

\subsection{Aggregate verdict on the 65-sub-basis sweep}\label{sec:results-65}

The canonical sweep
\texttt{harness/sweep\_output/m32b\_empirical\_sweep.jsonl}
(frozen at \texttt{gold/M3} = \texttt{9c2702d}) records
$65/65$
sub-basis verdicts of cascade-stable null, with the per-tier verification
classes summarized in Table~\ref{tab:agg}.

\begin{table}[h]
\centering
\caption{Aggregate verdict across the 65-sub-basis sweep.\label{tab:agg}}
\small
\begin{tabular}{p{0.36\textwidth}p{0.30\textwidth}p{0.16\textwidth}l}
\toprule
Quantity & Threshold & Measured & Status \\
\midrule
Cascade-stable null verdicts & $65/65$ & $65/65$ & PASS \\
\texttt{primary\_full} reproducibility,
  M3.2a$\leftrightarrow$M3.2b
  & $K$, $\Hrig$ identical at $P, 2P, 4P$
  & identical to $71$ digits & PASS \\
\texttt{primary\_full} verification class & \pc{} & \pc{} & PASS \\
$64$ empirical sub-bases verification class & \fsp{} & $64/64$ \fsp{} & PASS \\
PARI/GP second-leg per candidate
  & noise relation above $\Hempop$
  & $65/65$ & PASS \\
H10 pre-canonical full-regime dry-run
  & clean across all $65$
  & clean ($113$ s) & PASS \\
\bottomrule
\end{tabular}
\end{table}

No anomalies surfaced.
No halt conditions triggered.

\subsection{The primary cascade and its two-tier bounds}\label{sec:results-bounds}

The primary sub-basis is the full $\BDC$ at $n=15$ with
\texttt{maxcoeff}=$10^{70}$ and the cascade precision schedule
$\{P, 2P, 4P\} = \{2160, 4320, 8640\}$ dps with maxsteps schedule
$(100\,000, 80\,000, 50\,000)$.
The reproducibility check across two independent executions (M3.2a at commit
\texttt{d55ffbc}; M3.2b at commit \texttt{f621641}) returns bit-for-bit
identical outputs (Table~\ref{tab:cascade}).

\begin{table}[h]
\centering
\caption{Primary cascade outcomes, identical between M3.2a and M3.2b at every cascade leg
  (mpmath~1.3.0 / Python 3.12.10).\label{tab:cascade}}
\begin{tabular}{rrll}
\toprule
$P$ (dps) & $K$ iterations & $\mathrm{reported\_norm}$ (71-digit int) & $\Hrig$ \\
\midrule
$2160$  & $29\,363$ & $\underbrace{10360617603\ldots33854859767\!4}_{71\,\mathrm{digits}}$ & $1.0361\times 10^{72}$ \\
$4320$  & $29\,363$ & (identical) & $1.0361\times 10^{72}$ \\
$8640$  & $29\,363$ & (identical) & $1.0361\times 10^{72}$ \\
\bottomrule
\end{tabular}
\end{table}

The two-tier bounds for the primary cascade are
\begin{align*}
\Hempfo &= c\cdot 10^{P/(c\,n)}
       \;\approx\; 2.06 \cdot 10^{2160 / (2.06\cdot 15)}
       \;\approx\; 7.997\times 10^{69}
       & \text{(class \fsp{})}, \\
\Hempop &= \min(\Hempfo, 10^{70})
       \;=\; 7.997\times 10^{69} = \Hempfo
       & \text{(cap inactive at $n=15$)}, \\
\Hrig   &= 1.0361\times 10^{72}
       & \text{(class \pc{}; Eq.~\eqref{eq:Hrig})}.
\end{align*}

In words: no integer relation among the basis elements of $\BDC$ has all
coefficients $\le 7.997\times 10^{69}$ at the BBC-1997 empirical
confidence calibration of \cite[\S 2]{bailey1998}; and, by
\cite[Theorem~1 + Corollary~2]{fba1999} applied to the cascade's terminal
norm-bound certificate, every non-trivial integer relation has Euclidean
norm $\ge 1.0361\times 10^{72}$ (\pc{}-class), implying the
coefficient-height bound
$\max_{i}|m_{i}| \ge 1.0361\times 10^{72}/\sqrt{15} \approx 2.676\times 10^{71}$.

\subsection{Per-family aggregate}\label{sec:results-family}

The $65$ sub-bases group into six families
(Table~\ref{tab:family}).
The primary cascade ($n=15$) dominates the total wall-clock at $90.5\%$;
the remaining $64$ empirical candidates aggregate to $283.9$~s
($\sim 4.7$~min).
Small-$n$ families ($n=2, 3$) terminate fast with high cancellation-norm,
yielding $\Hrig$ statistic values in the $10^{72}$--$10^{73}$ range; mid-$n$
families ($n=8, 9$) run under the empirical-tier maxsteps schedule and
yield $\Hrig$ statistic values materially below $\Hempop$.
For all $64$ empirical sub-bases the predicate verification class is
\fsp{} (set by the maxsteps schedule, per \S~\ref{sec:h9}), independent of
the reported $\Hrig$ statistic; only the primary $n=15$ sub-basis carries
the \pc{} class.

\begin{table}[h]
\centering
\caption{Per-family aggregate over the 65-sub-basis sweep.
  The $\Hrig$ statistic is reported per record (Theorem~1 certificate at
  termination); the verification class follows the maxsteps schedule
  (\S~\ref{sec:h9}).\label{tab:family}}
\small
\begin{tabular}{lrrrll}
\toprule
Family & $n$ & count & $\Sigma$~wall-clock & $\Hrig$ median & verification class \\
\midrule
\texttt{primary\_full}             & $15$ & $1$ & $2693.8$ s & $1.04\times 10^{72}$ & \pc{} \\
\texttt{complement\_plus\_K0\_k}    & $9$  & $7$ & $229.8$ s  & $1.26\times 10^{16}$ & \fsp{} \\
\texttt{full\_complement}          & $8$  & $1$ & $27.0$ s   & $1.16\times 10^{21}$ & \fsp{} \\
\texttt{triplet\_log\_*}           & $3$  & $21$ & $21.4$ s & $1.17\times 10^{72}$ & \fsp{} \\
\texttt{pair\_bilinear\_*}         & $2$  & $21$ & $3.5$ s  & $2.38\times 10^{72}$ & \fsp{} \\
\texttt{pair\_log\_*}              & $2$  & $14$ & $2.3$ s  & $2.34\times 10^{72}$ & \fsp{} \\
\midrule
\textbf{Total}                     & ---  & $65$ & $2977.8$~s ($49.6$~min) & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

The wall-clock total ($49.6$ min) is approximately $30\%$ under our
$70$--$90$ min pre-execution estimate, dominated by the primary $n=15$
cascade.

\subsection{PARI/GP independent corroboration}\label{sec:results-gp}

For each of the $65$ sub-bases, the harness runs an independent
\texttt{gp lindep} second leg on the same basis at the same precision.
On every sub-basis, \texttt{gp lindep} returns either no relation or a
relation whose largest coefficient strictly exceeds the empirical operational
bound $\Hempop$; the cascade-stable null is corroborated independently.
This addresses the concern that \texttt{mpmath.pslq} and \texttt{gp lindep},
while implementing closely related algorithms (PSLQ in \texttt{mpmath};
LLL-based \texttt{lindep} in PARI/GP), might both miss a relation
through a shared algorithmic pathology; on the present basis this concern
does not materialize.

\subsection{Reproducibility of the cascade}\label{sec:repro-cascade}

The reproducibility check
$\text{M3.2a}\leftrightarrow\text{M3.2b}$
returns bit-for-bit identical outputs at every cascade leg:
$K = 29\,363$ iterations at all three precisions, identical $71$-digit
\texttt{reported\_norm} value, identical $\Hrig$.
This empirically confirms determinism of \texttt{mpmath.pslq} at $n=15$
across a $4\times$ precision range and two independent executions on the
build used here.
The determinism check was operator-mandated post-U-MISSION-N: any
non-reproducibility would have indicated non-determinism in the algorithm
that would affect the verification-class assignment.

%======================================================================
\section{Discussion}\label{sec:discussion}
%======================================================================

\subsection{Basis-class distinction: apples-to-stronger-apples
   with BBC~1997}\label{sec:discussion-apples}

We \emph{do not} claim a bound improvement on the BBC~1997 basis.
BBC~1997 \S 4 Test~1 tested EF1 (the pure-power family
$\{1, \K, \ldots, \K^{50}\}$ at $D=50$) at $H \le 10^{70}$ and $7350$ dps;
the present work tests the full basis $\BDC$
($D=6$, $|C|=7$, $n=15$, which contains both EF1 at $D{\le}6$ and the
named-open EF1-complement rows $\{\log\K\} \cup \{\K \cdot c\}$) at
$P=2160$ dps.
The bases differ in two structural respects --- EF1 truncation and
EF1-complement inclusion --- so a direct
``we improve BBC's $10^{70}$ to $10^{72}$'' framing would be
apples-to-apples on bases that are not the same and is therefore avoided.
The honest comparison is:
\begin{enumerate}[label=(\roman*),itemsep=2pt,topsep=2pt]
\item BBC~1997 produced a single-tier empirical null on EF1 at
  $H = 10^{70}$, sufficient to rule out a low-degree polynomial relation
  with bounded height on the pure-power basis.
\item The present work produces a two-tier null on $\BDC$ (which
  includes EF1 at $D{\le}6$ and adds the EF1-complement): empirical
  $\Hempop \approx 7.997\times 10^{69}$ on coefficient height
  (\fsp{}, BBC-class at the primary $n=15$ sub-basis) and rigorous
  Euclidean-norm bound
  $\Hrig = 1.0361\times 10^{72}$
  (\pc{}, FBA-class; implied height
  $\max_{i}|m_{i}| \ge 2.676\times 10^{71}$).
  The rigorous tier is the methodological strengthening; the
  EF1-complement inclusion is the named-open basis-class extension.
\end{enumerate}
A future apples-to-apples comparison would test a union basis that
preserves BBC's $D=50$ pure-power tower and adds the EF1-complement,
giving dimension $n = (D{+}1) + 1 + |C| = 51 + 1 + 7 = 59$.
The wall-clock cost scales roughly as
$\sim 59^{3}/15^{3} \approx 61\times$
per cascade step, which is feasible on an extended budget but is outside
the present scope.

\subsection{Operational-bound capping observation}\label{sec:discussion-capping}

Across the $64$ empirical sub-bases of
\texttt{m32b\_empirical\_sweep.jsonl},
the canonical operational empirical bound
$\Hempop = \min(c\cdot 10^{P/(c\,n)},\; 10^{\log_{10}\textsf{maxcoeff}})$
differs from the uncapped BBC scaling formula
$\Hempfo = c\cdot 10^{P/(c\,n)}$
at every $n \le 14$ sub-basis: at $P=2160$ dps, $c \approx 2.06$,
$\textsf{maxcoeff}=10^{70}$, the formula yields
$\approx 10^{70}$
exactly at $n \approx 14.97 \approx 15$.
At $n = 15$ the cap is inactive ($\Hempop = \Hempfo \approx 7.997\times 10^{69}$).
At small $n$ ($n=2, 3$), the formula evaluates well above the
\textsf{maxcoeff} bound ($\sim 10^{524}$ and $\sim 10^{349}$ respectively);
reporting these as operational bounds would overclaim the searched range.
We retain both values in the JSONL output: $\Hempop$ for predicate
evaluation and table reporting, $\Hempfo$ for transparency about where
the empirical extrapolation diverges from the searched range.

This is a small refinement to BBC-class empirical-tier reporting at
parameter regimes where the scaling formula extrapolates outside the
algorithm's \textsf{maxcoeff} bound.
The refinement is grounded in the ``somewhat greater than''
hedge of \cite[\S 2]{bailey1998}: the empirical scaling is stated as a rule
of practice, not as a tight bound; reporting it as if it were a tight bound
at parameter regimes outside the search range is the failure mode this
capping clause addresses.

\subsection{Capability gap: symbolic closure of the null result is
   fundamental}\label{sec:m4-gap}

Symbolic closure of the M3 null result was attempted via a survey of seven
candidate structural arguments
(Lindemann--Weierstrass, Schanuel, Nesterenko, Mahler-measure, Galois,
non-GKW continued-fraction-theoretic, and height theory)
and a four-path probe in \texttt{SymPy} 1.14.0
(\texttt{is\_transcendental}/\texttt{is\_irrational}, \texttt{nsimplify}
against a named-constants basis, Groebner basis on the symbolic basis $\BDC$,
and transcendence-theorem applicability check).
Every candidate failed at the same root: $\K$'s transcendence status is
itself the major open question in this corner of the literature, and any
structural certificate strong enough to rule out integer relations in
$\BDC$ at relation Euclidean norm
$\le 1.036\times 10^{72}$ would imply progress on that
question.
We classify this gap as fundamental: no known structural result is strong
enough --- not merely a machinery-availability problem --- and the null
result therefore stands on numerical and rigorous-bound evidence per the
two-tier predicate
($\Hempop \approx 7.997\times 10^{69}$ \fsp{};
$\Hrig = 1.036\times 10^{72}$ \pc{} on the Euclidean norm).

\paragraph{Sub-classification of the failure modes.}
The seven candidates fail for two qualitatively different reasons.
Six of seven are structurally unavailable on external grounds alone:
Lindemann--Weierstrass requires $\K = e^{\alpha}$ for algebraic $\alpha$,
which is not known to hold; Schanuel is unproven, and a clean
$\K = \exp(z)$ representation for explicit $\mathbb{Q}$-linear $z$ is not
known; Nesterenko's 1996 method covers $\pi, e^{\pi}, \Gamma(1/4)$ and has
no published extension to the Khinchin class; Mahler measure, Galois
theory, and height theory all require $\K$ algebraic with known minimal
polynomial, which is unknown.
The seventh (non-GKW CF-theoretic) is internally scope-ceded under a
mission-procedural binding, but is also structurally unavailable externally:
no non-GKW continued-fraction-theoretic result strong enough to constrain
integer-relation existence in $\BDC$ is published.
The fundamental classification is therefore based primarily on the
structural unavailability of the six external candidates, with the
seventh as a double-blocked corroborating case.

\paragraph{What we are not claiming.}
We are not claiming structural non-existence of integer relations on
$\BDC$, nor a structural closure of the M3 null.
The null result stands on its numerical evidence and rigorous-bound
proven-corollary application alone; the symbolic-closure attempt is
reported here for transparency about the limits of what numerical evidence
plus available structural theory can jointly establish for this constant
class.

%======================================================================
\appendix

\section{Reproducibility}\label{app:reproducibility}
%======================================================================

\paragraph{Repository and gold tags.}
All canonical artifacts are hosted at
\url{https://github.com/papanokechi/khinchin-k0-bounded}
on \texttt{origin/main}, tagged in milestone order:
\texttt{gold/M1} (\texttt{15b216f}; target selection),
\texttt{gold/M2} (\texttt{ca9c989}; M2.3 predicate),
\texttt{gold/M3} (\texttt{9c2702d}; canonical JSONL outputs),
\texttt{gold/M4} (\texttt{fd13eeb}; capability-gap document),
\texttt{gold/M5} (\texttt{208f6fc}; Lean~4 skeleton).
Tags are annotated; the manuscript snapshot is at the commit cited in the
title-page footnote.

\paragraph{Environment.}
The canonical environment lock is in
\texttt{env/M1.lock}
(generated at the M1.3 gold freeze):
Microsoft Windows 11 Pro Insider Preview 10.0.29585; Python 3.12.10;
\texttt{mpmath} 1.3.0; \texttt{sympy} 1.14.0; \texttt{numpy} 2.4.4;
\texttt{gmpy2} 2.3.0; Lean 4.29.1; Lake 5.0.0-src+f72c35b; Mathlib4
v4.14.0; PARI/GP 2.18.1.

\paragraph{Commands.}
\begin{lstlisting}
# M3.2a primary cascade only (n=15 full basis):
python harness/sweep.py --m32-primary-measurement --m32-primary-greenlighted

# M3.2b empirical sweep (65 sub-bases, ~50 min on a 2024-class CPU):
python harness/sweep.py --full --m32-full-greenlighted

# H10 pre-canonical full-regime dry-run (113 s wall-clock):
python harness/sweep.py --m31-extended-dry-run

# Lean 4 statement-shape check (post `lake update`):
cd m5 && lake build M5
cd m5 && lake env lean PrintAxioms.lean   # reproduces _print_axioms_output.txt
\end{lstlisting}

\paragraph{Paper-read primary sources (SHA-256 hashes).}
The following primary sources were paper-read and their digital copies
hashed at retrieval:

\begin{longtable}{p{0.30\textwidth} p{0.10\textwidth} p{0.50\textwidth}}
\toprule
Source & lit-NNN & SHA-256 (file) \\
\midrule
\endhead
Signature paper \cite{papanokechi2026signature} & lit-001 & (operator-authored, MIT-licensed repo snapshot) \\
BBC 1997 \cite{bbc1997} & lit-002 & (paper-read verified; hash in \texttt{literature/claims.jsonl}) \\
FBA 1999 \cite{fba1999} & lit-009 & \texttt{3E330BC1...12890B5} (\texttt{cpslq.pdf}, $218\,997$ B) \\
Bailey 1998 \S 2 (PSLQ) \cite{bailey1998} & lit-010 & \texttt{5E435CAF...4895} (\texttt{node3.html}, $11\,344$ B); \texttt{8BEB376B...6A00} (\texttt{paper.html}, $2\,123$ B) \\
\bottomrule
\end{longtable}

\paragraph{Canonical artifacts.}
The two load-bearing JSONL files are
\texttt{harness/sweep\_output/m32a\_primary\_cascade.jsonl} (M3.2a, $5\,649$ B)
and
\texttt{harness/sweep\_output/m32b\_empirical\_sweep.jsonl} (M3.2b, $363\,709$ B);
both are frozen at \texttt{gold/M3} = \texttt{9c2702d}.
The aggregate-verdict audit produced by
\texttt{harness/\_audit\_m32b\_summary.py}
on the same data is saved at
\texttt{harness/sweep\_output/m32b\_summary.md}
(also at \texttt{gold/M3}).

\paragraph{Wall-clock.}
On a single core of an Intel-class 2024 laptop CPU with $16$~GB RAM:
M3.2a primary cascade $\approx 66.5$~min; M3.2b full empirical sweep
$\approx 49.6$~min ($90.5\%$ on the primary $n{=}15$ cascade,
$\sim 4.7$~min on the $64$ empirical sub-bases);
H10 pre-canonical dry-run $\approx 113$~s.

%======================================================================
\section{The AEAL heuristic-accumulation methodology}\label{app:aeal}
%======================================================================

The present work was conducted under an explicit-evidence-acceptance-and-logging
(AEAL) discipline: every load-bearing claim is required to carry an
explicit evidence class, every halt event is logged, every heuristic is
named and dated, and any change to the bounded hypothesis incurs a
mutation-log entry.
The discipline was iteratively shaped by the work as it proceeded; the
present appendix records the heuristic set that crystallized over the
mission's six milestones M1--M5 plus the present M6, as a small but real
methodological contribution distinct from the $\K$ result.

\subsection{Heuristic accumulation H1--H10}\label{sec:aeal-heuristics}

The ten heuristics canonical to this work are:
\begin{description}[itemsep=2pt,topsep=2pt]
\item[H1.] PSLQ cascading-precision triage:
  Any candidate relation is verified by re-running PSLQ at $2\times$ and
  $4\times$ precision with the same coefficient bound; transient false
  positives at low precision are rejected.
\item[H2.] Literature-ledger prioritization for the bounded survey:
  Literature claims that bound the central hypothesis are loaded into the
  ledger first; tangential citations are not pursued.
\item[H3.] Stall-diagnostic timing within wall-clock caps:
  A scheduled stall-diagnostic at fixed wall-clock checkpoints separates
  budget-exhaustion from algorithmic stalls.
\item[H4.] Capability-gap escalation discipline:
  If a step of the mission requires machinery not in the declared
  capability stack, the gap is documented (not papered over) and the
  mission halts for operator review.
\item[H5.] Mutation-log entry discipline:
  Any change to the bounded hypothesis (basis shape, predicate form,
  success criterion) incurs a mutation-log entry; field-map updates
  (citation strength, status promotions within an established taxonomy)
  do not consume mutation budget.
\item[H6.] Namespace audit on independence scoring:
  Independence claims between two basis classes are audited at the
  namespace level (content / machinery / attribution).
\item[H7.] Functional verification on capability claims:
  A claimed capability (a tool, an algorithm, a package) is verified by
  function-call rather than name resolution alone.
\item[H8.] Paper-read verification on dependency literature claims:
  Load-bearing literature claims are verified by direct reading of the
  primary source (paper, preprint, supplementary material); web aggregators,
  citation databases, and LLM-mediated summaries are not sufficient.
\item[H9.] Theorem-vs-heuristic classification on cited bounds:
  Cited numerical bounds are reported under a four-class taxonomy
  (\rt{}, \pc{}, \fsp{}, \eh{}), with the class explicit in the manuscript
  and in the canonical JSONL output.
\item[H10.] Full-regime dry-run mandatory before canonical execution:
  Any sweep introducing a new $(P, n, \text{basis structure})$ regime
  requires a full-regime dry-run at canonical precision before canonical
  execution; the dry-run catches code paths that exist but have never been
  exercised at canonical scale, distinct from H7's ``tool isn't installed
  but name resolves.''
\end{description}

Six of these ten (H6--H10) were installed mid-mission in response to
specific halt events: H6 from a target-shortlist overlap audit; H7 from
a capability-probe false-positive on a PARI/GP install state; H8 from a
literature-fidelity catch on an AI-aggregated claim later refuted by
paper-read; H9 from a heuristic-vs-theorem catch on the
$H \approx 10^{P/n}$
scaling formula; H10 from a harness-execution catch when a code path was
exercised at canonical precision for the first time.

\subsection{Bidirectional verification: heuristics apply to operator
   framing as well as agent output}\label{sec:aeal-bidirectional}

A property of the heuristic set that emerged during the mission is its
bidirectional application: H8 fires not only when the agent cites a
literature claim, but also when the operator's framing of a claim is
under examination.
For example, the resolution of one halt event required determining whether
a claim that ``FBA 1999 states $H \approx 10^{P/n}$ as a theorem'' was
operator-introduced or agent-introduced; H8 paper-read on
\cite{fba1999} established that neither party had cited the claim as a
theorem of FBA, and the H9 classification was upgraded accordingly.
The bidirectionality is structural: the AEAL discipline is not an
agent-fidelity audit; it is a joint operator-and-agent fidelity audit
against canonical artifacts.

\subsection{Health-score retrospective}\label{sec:aeal-health}

We close with four health-score observations across the full mission.
The claim-to-sweep ratio (load-bearing claims in the manuscript per
candidate sub-basis tested) is approximately $5/65$: the manuscript
makes few claims, the sweep tests many candidates.
The reproduce-command coverage is approximately $100\%$: every numerical
claim in the manuscript has a corresponding canonical command in
Appendix~\ref{app:reproducibility}.
The capability-gap honesty is positive: a fundamental gap is reported as
such in Section~\ref{sec:m4-gap} rather than papered over with additional
numerics.
The literature-fidelity honesty is positive: two paper-read events
(\cite{fba1999} mid-mission; \cite{bailey1998} at M6 Step~1) upgraded the
manuscript's empirical and rigorous-tier framings against the
canonical primary sources, in both cases strengthening the framing without
weakening any verification class.

% ---------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{references}

\end{document}
